---
title: "BM_Calc_Test"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BM_Calc_Test}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(RapidRicker)
```





This function calculates Ricker Model parameters for spawner-recruit data with a simple linear fit of log(R/S) ~ S implemented with an MCMC using the jags() function from the R2jags package. For details such as model form and variable definitions, refer to \href{https://github.com/SOLV-Code/RapidRicker/wiki/MCMC-Using-R2Jags}{this wiki page}. Note that these are designed as quick fits to support initial exploration of Bayesian posteriors,  to support a pre-screeing of assumptions before setting up a proper model fit. Some standard diagnostics can be part of the output, but the function does NOT do any quality control for you. Also, the default priors and inits may not make sense for your data. There are many tutorials available online for linear model fits and associated diagnostics using R2jags (e.g. \href{http://biometry.github.io/APES//LectureNotes/StatsCafe/Linear_models_jags.html}{here},\href{https://rpubs.com/corey_sparks/30893}{here}, and \href{https://rpubs.com/Niko/332320}{here}).
Also calculates standard biological benchmarks (Smsy, Seq, Smax, Umsy). Benchmark calculations were adapted from BUGS code used in Miller & Pestal (2020), available \href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_035-eng.pdf}{here}.
Two versions for some BM are produced: "_h" = Hilborn Proxy (\href{https://cdnsciencepub.com/doi/pdf/10.1139/f85-230}{Hilborn 1985}) and "_p" = Peterman Proxy" (\href{https://cdnsciencepub.com/doi/pdf/10.1139/f99-204}{Peterman et al. 2000}). Note: This requires installing JAGS from \href{https://sourceforge.net/projects/mcmc-jags/files/latest/download}{here}.
@param sr_obj a data frame with Spn,Rec (actual numbers, not thousands or  millions) for the MCMC and logRpS for the deterministic fit (Data for 1 Stock!). Other variables can be there but are not used (RpS, Qual, ExpF etc)
@param sr.scale an integer value used to rescale the Spn and Rec variables in sr_obj, prior to the MCMC fit, default = 10^6 (i.e. convert to millions). NOTE: If sr.scale is different from 1, then
the benchmark estimates are scaled back, but the MCMC estimates of alpha and beta will be in different units then the alpha and beta estimates from the deterministic fit.










